A Survey of Range-Only SLAM Techniques and Sensors

### 2018-11-07 Paper.tex
Slight rewording

	A common focus of many recent papers has been the utilization of beacons for more than just robot to beacon range measurements. Many implementations now seek to measure the distance between beacons and incorporate those measurements into existing EKF algorithms.

>>>>

	A common focus of many recent papers has been the utilization of beacons for more than just robot to beacon range measurements. Many implementations now have beacons measure ranges to other beacons in addition to the robot. These beacon to beacon range measurements are then incorporated into existing EKF algorithms.
